Jane, John … Leslie? A Historical Method for Algorithmic Gender Detection

### 2014-09-18 article.Rmd
Proportion of dissertations

```{r load-libraries, include=FALSE}
library(genderdata)
library(gender)
library(dplyr)
library(ggplot2)
library(mullenMisc)
library(knitr)
library(stringr)
library(scales)

@@

![Number of dissertations by gender](img/plot-gender.png)

@@

![Proportion of dissertations for each gender](img/dissertations-by-gender-proportion.png)

>>>>

```{r load-libraries, include=FALSE}
library(genderdata)
library(gender)
library(dplyr)
library(ggplot2)
library(mullenMisc)
library(knitr)
library(stringr)
library(scales)
library(tidyr)

@@

```{r}
short_scale <- scale_x_continuous(breaks = seq(1950, 2010, 10),
                                  labels = seq(1950, 2010, 10),
                                  limits = c(1950, 2012))

diss_predicted %>%
  ggplot(aes(x = year, fill = gender_author)) + 
  geom_bar(binwidth = 1) +
  ggtitle("Dissertations about History by Gender, 1950-2012") +
  xlab(NULL) + ylab(NULL) +
  short_scale + theme(legend.position = "bottom") +
  scale_fill_discrete(name = "",
                      labels = c("Female", "Male"))
```

@@

```{r}
diss_predicted %>%
  select(year, gender_author) %>%
  filter(year >= 1950) %>%
  group_by(year, gender_author) %>%
  summarize(n = n()) %>%
  spread(gender_author, n) %>% 
  mutate(female_proportion = female / (female + male),
         male_proportion = male / (female + male)) %>% 
  select(female_proportion, male_proportion, year) %>%
  gather(gender, proportion, -year) %>% 
  ggplot(aes(x = year, y = proportion, fill = gender)) + 
  geom_bar(binwidth = 1, stat = "identity") +
  ggtitle("Proportion of Dissertations about History by Gender, 1950-2012") +
  xlab(NULL) + ylab(NULL) +
  short_scale + theme(legend.position = "bottom") +
  geom_hline(yintercept = 0.5) +
  scale_fill_discrete(name = "",
                      labels = c("Female", "Male"))
```
